The Distributional Impacts of the Electricity Transition on Pollution Exposure

### 2024-12-09 MIP_Downscaled.tex

>>>>

The cost of deaths can be a sizable portion of overall system costs.  In figure \ref{CostsBarchart}, we plot total costs (in NPV) across scenarios, including a component for monetized costs of air pollution deaths.  We use EPA's Value of Statistical Life, which is currently $\$7.4 million$ in U.S. $\$ 2006$, which we inflation-adjust to $\$11.51$ million in 2024 dollars.

\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{Figures/Output/Costs_Barchart_GenX.png}
    \caption{Caption}
    \label{CostsBarchart}
\end{figure}
